ms_figures

### 2023-02-06 ms_figures.Rmd

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
```

@@

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(x = "", y = "Trade (million t, live weight)", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "none",
        strip.background = element_blank()) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free")

@@

```{r fig4b}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

@@

@@

fig4c
```
```{r fig4, fig.height = 3, fig.width = 3}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )

>>>>

library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
```

@@

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(x = "", y = "Trade (million t, live weight)", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "none",
        strip.background = element_blank(), 
        plot.margin = margin(t = 8, r = 8, l = 2, unit = "mm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free")

fig2b <- ggdraw(fig2b) +
  draw_label("Exporting region", x = 0.975, y = 0.5, angle = 270) +
  draw_label("Importing region", x = 0.5, y = 0.975)

@@

```{r fig4b_old, eval=FALSE}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

@@

```{r fig4b}
# NOTE: Rahul - we need to have the correct file read in here. For reference, the file currently generating this and the new fig 4d is "/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv"
# I am not sure we should go with these colors, but didn't have time to keep messing with this
# These comments also apply to the new fig4c

fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

```{r fig4c}
fig4c <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

fig4c
```

@@

fig4c
```

```{r fig4, fig.height = 3, fig.width = 3}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )
